Economic Evaluation of Geographically Weighted Regression Analysis for Site-specific Nitrogen Management

### 2023-06-23 Writing/JAAEA/1stRoundRevision/reply_to_reviewer_2.rmd

<br>

<span style = "color: blue;">General Comments</span>

<span style = "color: blue;">To some extent, this research is related to studies that examine the “value” of forecasting models by assessing their measure of inaccuracy. Given that determining the value of general regression methodologies is not overly common in the relevant literature here, why not add 1-2 paragraphs that ties your study to other studies that measure the “value” of certain econometric techniques?
</span>  
Reply: Thank you for bringing up this important point. A significant aspect that sets this study apart from many previous studies lies in the evaluation of econometric models, where this study's measures are not based on the statistical accuracy of parameter estimates, but rather on the ultimate economic returns generated by the models. To emphasize this aspect, we have included an additional paragraph in the "Discussion and Conclusions" section (page x, lines xxx). It is worth noting that we were unable to identify a specific body of literature that exclusively focuses on assessing the value of general regression models. However, it is customary in the development of econometric models to evaluate their performance using statistical accuracy measures such as bias, mean squared error, and type I error, based on simulation data. We have referenced a few relevant studies of this nature to underscore the distinction of our economic value assessment approach.

@@

<span style = "color: blue;">Where is there no in-text reference to, or explanation of, Figure 4? I do not know what to make of this lone figure.</span>  
Reply: We sincerely apologize for this oversight. The figure was originally included to compare the estimated and true GWR coefficients $\beta_1$ and $\beta_2$. However, as we have already compared the estimated and true EONRs in the subsequent figure, the coefficient comparisons are no longer necessary. Regrettably, we forgot to remove it from the final manuscript. We have now rectified this mistake and removed the figure accordingly. Thank you for bringing it to our attention.
(__Taro: I removed that figure. Is it OK? Or you still want to keep it and say something about it?__)

@@

<span style = "color: blue;">P. 5, lines 89-90: By this point, it would have been useful to add 1-2 sentences or a footnote about parallels with nonparametric estimators. Using multiple data points to derive local estimates, as in kernel density estimation, is nothing new. It would be helpful to provide more background on this. More broadly, at this point, besides the economics, why should we care about GWR relative to other spatial statistics methods?</span>  
Reply: We agree with the reviewer's comment that there are many nonparametric estimators that can estimate local yield responses, among which GWR is only one of them. However, the goal of this study is not to compare GWR with other estimators or to advocate the use of GWR. As stated  in the introduction section (page 1, lines 41-42xx; page 2, lines 61-65xx), the background of this study is that GWR model has gained attention in developing site-specific input recommendations due to its minimum requirement of costly field data collection. Our interest is to further test whether GWR is truly economically viable in this application and provide guidance for precision farming practice. The current study does not intend to involve other spatial statistics methods. But we do have plans to conduct similar simulation-based economic evaluations of other local response estimation methods (such as the spatial kriging smoothing) in future research.

<span style = "color: blue;">P. 9, line 192: Here, do you mean that you set the 1370 kg ha-1 to be the square root of the sill variances?</span>  
Reply: We apologize for the typo. Yes, it should be the square root of the sill variances since 1379 kg ha$^{-1}$ was the mean of standard deviations. Thank you for pointing out this typo. We have corrected that statement (see page x, line xx in the revised manuscript).

<span style = "color: blue;">P. 11, line 220: At the first mention of shape-constrained additive models (SCAM), there should be a few sentences of explanation, either in the body or as a footnote. Even after the partial explanation on lines 232-233, it is still somewhat unclear and warrants more detail. The general readers of JAAEA are likely to not know, either.</span>  
Reply: Thank you for the suggestion. We added a few more explanations of the SCAM (see page xx, lines xxx of the revised manuscript) to make it more clear to the general JAAEA readers that it is a regression model that can fit a more flexible and non-linear response relationship, and also allows for shape constraints that can incorporate prior knowledge or theories.

@@

<span style = "color: blue;">Pp. 11-12, lines 238-245: To check, l=K, i.e., the total number of splines from the equation on line 238 equals the total number of splines used for f ̂_SCAM (∙)? If so, use the same notation.</span>  
Reply: Thank you for pointing out this typo of notations. Yes, the $l$ and $k$ should be the same. We corrected the notations to use $k$ in the revised manuscript.

<span style = "color: blue;">P. 13, lines 268-270: How robust are the N ̂_(GWR-T,j )^*rates to variations in the AIC-chosen bandwidth parameters? More information about this needs to be provided.</span>  
Reply: If we have correctly understood the question, it pertains to the robustness of GWR estimates with respect to bandwidth selection. We acknowledge that choosing the appropriate bandwidth is a critical step in GWR estimation, and the literature offers numerous methods for bandwidth selection. In our study, we employed the corrected version of the AIC approach as proposed by Fotheringham et al. [@fotheringham2017multiscale; @lu2017geographically] to determine the optimal bandwidth. This approach is widely used in practice and aligns with the methodology employed by Rakshit et al. [@rakshit2020] and Trevisan et al. [@trevisan2021spatial], thereby ensuring consistency in our simulation evaluations.

As the corrected AIC method results in a unique bandwidth, we did not conduct additional robustness checks on alternative bandwidth values. While we acknowledge that GWR results may vary when using different bandwidths, selecting bandwidths other than the one determined by the AIC approach could introduce arbitrariness. Nevertheless, we have provided additional discussions about bandwidth selection in more depth in the revised manuscript on page x, lines xxx to provide more details and clarifications.

<span style = "color: blue;">P. 15, lines 303-305: Why are the numbers from these sentences blank? In particular, the median benefit of VRA under GWRR is ? and the median benefit of VRA under GWRT is…?</span>  
Reply: We apologize for the oversight in the sentences with blank numbers. We have rectified the issue by correcting the typos and providing the missing numbers. You can find the updated information on page x, line xx in the revised manuscript. Thank you for bringing this to our attention.

<span style = "color: blue;">P. 15: You first discuss figure 6 and then move to figure 5. Put all figures in order.</span>  
Reply: Thank you for identifying the incorrect order of Figures 5 and 6. We apologize for the mistake, and we have corrected the order of the figures accordingly. The revised manuscript now reflects the correct sequence of Figures 5 and 6.

@@

<br>

<span style = "color: blue;">
Writing
</span>

<span style = "color: blue;">P. 2, line 45: This should be “data are”, not “data is”. </span>  
Reply: This grammar error was corrected. The new sentence is now on page xx, line xx of the revised manuscript.

<span style = "color: blue;">P. 2, line 52: Basically or actually? Vagueness here makes it difficult to assess the degree to which OSU’s calculators are being used directly. </span>  
Reply: The term "basically" used in that context does appear informal and imprecise. In the revised manuscript, we have removed the term "basically" (see page x, line xxx) to ensure clarity and eliminate any potential confusion.

<span style = "color: blue;">P. 2, line 54: To avoid confusing a general agricultural economics audience, I would use an abbreviation other than Rx for site-specific recommendations. </span>  
Reply: In precision agriculture, the site-specific recommendation map is commonly referred to as a "prescription" or denoted as "$R_x$" by both researchers and industry professionals. While there may be other abbreviations in use, they are not as widely recognized as "$R_x$". To ensure clarity for readers who may not be familiar with precision agriculture terminology, we have included a brief note explaining that "$R_x$" represents "prescription" when it is first mentioned (page x, line xxx in the revised manuscript). This clarification aims to make the meaning of the abbreviation clear to a broader agricultural economics audience.

<span style = "color: blue;">P. 2, lines 49-60: All of these current commercial examples would work better as a footnote as they may become inaccurate in the next 3-10 years (or fewer). </span>  
Reply: Thank you for the suggestion. We agree that placing the commercial examples in a footnote is a better approach. As per your suggestion, all the relevant content has been moved to footnote 1 on page xx of the revised manuscript.

<span style = "color: blue;">P. 5, lines 91-114: This page-long paragraph should be split up into at least two paragraphs. The length is taxing. I would consider starting a new paragraph with the sentence beginning on line 97.</span>  
Reply: Thank you for the suggestion. We have followed this suggestion and divided the discussion into two paragraphs. The second paragraph now begins on page x, line xx. Additionally, we have made slight wording changes to the beginning of this paragraph to enhance clarity and coherence.

<span style = "color: blue;">P. 7, line 137: This comment should have been removed by the authors prior to manuscript submission.</span>  
Reply: This typo has been removed. Thank you for bring it to our attention.

<span style = "color: blue;">P. 9, line 189: The acronym DIFM is used before it’s spelled out in the sentence, but you should spell it out first and then use the acronym. </span>  
Reply: Thank you for pointing out this writing issue. We have addressed it by placing the acronym DIFM after its full name, as suggested. The revised placement can be found on page x, line xx.

<span style = "color: blue;">P. 10, line 212: The (j,k) index should be subscripted here.</span>  
Reply: We greatly appreciate the reviewer's meticulous review of the manuscript and for finding this typo. We have corrected it to use subscript notation (see page x, line xx). Furthermore, to eliminate the duplication of the spline index $k$, we have updated the cell index notation to ($j$, $i$) both in this section and throughout the rest of the manuscript.

@@

<span style = "color: blue;">P. 11, line 221: The second “and” should be “an”. </span>  
Reply: The typo is corrected. Thank you so much for finding this typo.

<span style = "color: blue;">P. 11, line 232: Are you using one shape constraint or more than one shape constraint? The language here really matters so as to avoid confusion on the part of the readers.</span>  
Reply: The model described here is a single yield response function for the full field. In other words, there is only one uniform response rather than variable responses. We acknowledge that the language used may have caused confusion regarding whether it refers to a "single" response function or a "single" shape constraint. To address this concern and eliminate any ambiguity, we have removed the term "single" from the manuscript (see page x, line xx in the revised version).

<span style = "color: blue;">P. 11, line 235: It seems that 1-2 citations could be added (or are missing) after “well substantiated by agronomic research.”</span>  
Reply: We followed the comment and added two citations of agronomic studies to support this statement (see page x, line xx in the revised manuscript).

<span style = "color: blue;">P. 12, line 253: I know what you mean by the notation f ̂_(GWR-R,j) (N), but the hyphen in the notation almost seems like a subtraction sign. I would recommend changing GWR-R and GWR-T to GWRR and GWRT and then having superscripts here. That is, f ̂_j^GWRR (∙) and f ̂_j^GWRT (∙).</span>  
Reply: Thank you for the recommendation. We also agree that "GWRR" and "GWRT" appear more concise than "GWR-R" and "GWR-T", and have made the changes as recommended. Additionally, we have placed all model names (GWR and SCAM) in superscripts in the equations. We appreciate the reviewer's comment, which has helped us improve the consistency of our notations across the manuscript.

<span style = "color: blue;">P. 13, line 271: In keeping with your past usage, you should make sure the acronym SCAM is in uppercase throughout the text.</span>  
Reply: Thank you for pointing out this formatting error. We have corrected the issue by ensuring that the acronym "SCAM" is consistently written in uppercase throughout the text. Additionally, we have capitalized all acronyms in equations as well.

<span style = "color: blue;">P. 15, line 304: “but the its benefit is even negative at when the” should have the typos/redundant wording removed.</span>  
Reply: Thank you for pointing out those typos. They have all been corrected (see page x, line xx in the revised manuscript).

<span style = "color: blue;">P. 17, line 335: Figure 0?</span>  
Reply: We apologize for the typographical error. It should be Figure x. (__Taro: Which figure are you referring to here? I don't think it should be Figure 5.__)

<span style = "color: blue;">P. 18, line 362: Section title should just be “Discussion”. </span>  
Reply: The title has been changed to “Discussion”. Furthermore, we combined this section with the conclusions section, and the new title is "Discussion and conclusions".

<span style = "color: blue;">P. 34, Figure 8 horizontal axis label: “Estiamated” should be “Estimated”. </span>
Reply: We greatly appreciate the reviewer for identifying this typo. It was corrected in the revised manuscript.

<span style = "color: blue;">Pp. 19-20, lines 398-400: Can this sentence be sharpened? Right now, it is a bit too vague to be completely useful as a guide to researchers in this area. Specifically, what other statistical estimators should be reconsidered and how (specifically) should they be reassessed?</span>  
Reply: We sincerely appreciate the reviewer's feedback regarding the vagueness of this sentence. We added more details to explain that the other commonly used statistical methods in the site-specific yield response estimation literature include the regression with interaction terms of field characteristics, machine learning, etc. The assessment approach will be simulation-based evaluation that is similar to the one used in this study. (See page x, line xx in the revised manuscript.)

### 2023-06-23 Writing/manuscript_gwr.rmd
Reviewer 2 comments completed

However, deploying sophisticated sensors to gather field characteristics data is also costly, and the effects of their generation and use on farming profitability remains in question [@gardner2021economic]. Recognizing the significant costs of obtaining useful, high-resolution soil and field properties data, @trevisan2021spatial demonstrated a method of providing site-specific management recommendations without such data. They estimated site-specific yield response functions by applying GWR techniques on data from OFPEs [@bullock2019data], and reported dramatic results, estimating an average potential gain of \$65 ha$^{-1}$ from applying seed and N at optimal uniform rates (instead of at the rates the farmers would have chosen if not participating in the research), and an additional potential gain of \$58 ha$^{-1}$ when changing from optimal uniform application rates to optimal site-specific application rates. This is rather surprising given the often-reported poor statistical accuracy of GWR estimates [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation] and also much lower value of variable rate application over uniform rate application reported in previous studies (cite). @rakshit2020 also applied GWR to on-farm experiment data. However, while they did estimate site-specific yield response functions, they did not derive site-specific economically optimal nitrogen rates based on them, and thus did not conduct economic analysis, unlike @trevisan2021spatial. @evans2020assessment explored using GWR with a linear model specification to detect low- and high-response areas, but like @rakshit2020, they also did not estimate site-specific economically optimal nitrogen rates.

@@

The primary objective of this study is examine the degree and direction of bias in the estimation of the economic value of GWR-based site-specific nitrogen rate recommendations (or "variable rate application", VRA) when GWR model is specified as quadratic when the true yield response function follows the quadratic-plateau functional form. We evaluate two sets of GWR quadratic specifications used in @rakshit2020 and @trevisan2021spatial. Both of them assumed a quadratic response of yield to nitrogen rate ($N$). However, while @trevisan2021spatial estimated the coefficient on $N^2$ as a global parameter, @rakshit2020 estimated it locally for each point. At first, it appears that the specification used by @rakshit2020 is superior since it is more flexible than the specification used by @trevisan2021spatial. However, the flexibility can be a disadvantage rather than an advantage because the estimation of economically optimal nitrogen rate (EONR) is highly sensitive to the coefficient estimates on $N^2$, and GWR often provides inaccurate local estimation of that coefficient. It is critical to keep in mind that it is not our objective to measure the bias in the coefficient estimation by GWR, unlike [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation]. Rather, we are interested in the economic implications of the statistical inaccuracy in estimating the coefficients of the model in this study. As part of identifying bias in the estimation of the economic value of VRA based on the GWR approaches, we evaluate their actual values. Finally, we also evaluate their relative performances compared to uniform rate application (URA) based on shape-constrained additive model approach. It should be noted that the economical optimization in this study only includes farmers' private profit, while the environmental externalities (such as fertilizer runoff and leaching) are not considered.

@@

The field was 432m (72 cells) wide and 864m (144 cells) long, making its area 37.3 ha. Data from the 6-m-long headlands, side-lands (there are no transition zones on the north and south ends of the field), and 12-m-wide "transition zones" were not included in the data analyzed. In total there were 1440 subplots available for experimental data analysis. The index $j \in {1, 2, \dots, 1440}$ identifies the field's subplots, and the index $k \in {1, \dots , 6}$ identifies the cells within a subplot. The couplet $(j, k)$ is used to identify individual cells.

@@

An extensive literature examines the choice of functional form in yield response estimation [@cerrato1990comparison, @frank1990comparison, @bullock1994quadratic, @tembo2008crop]. Our simulation assume that each cell $(j, k)$'s "true" yield response function is assumed to follow the commonly-used quadratic-plateau functional form:

$$
\begin{equation} \tag{1}
y_{j,k} = f_{j, k} (N) = f(N, c_{j,k}) = 
  \begin{cases}
  \alpha_{j,k} + \beta_{j,k} N + \gamma_{j,k} N^2 + \varepsilon_{j,k} \, ,& N < \tau_{j,k} \\
  \alpha_{j,k} + \beta_{j,k} \tau_{j,k} + \gamma_{j,k} \tau_{j,k}^2 + \varepsilon_{j,k} \, ,& N \ge \tau_{j,k}
  \end{cases}
\end{equation}
$$

where $c_{j,k} = (\alpha_{j,k},\beta_{j,k},\gamma_{j,k},\tau_{j,k})$ is the vector of yield response function parameters. $\tau_{j,k}$ can be interpreted as the critical value of N rate at which cell $(j, k)$'s yield reaches its plateau, where yield no longer increases with N rate. $\varepsilon_{j, k}$ is a stochastic error term. The quadratic-plateau functional form implies a diminishing marginal product of N until a yield plateau, which are desirable properties for a yield response function [@frank1990comparison] and a pattern commonly observed in agronomic studies. Note that the cell-specific yield response function $f_{j, k} (N)$ is the reduced form of the meta response function $f$ when the characteristics vector takes on the value $c_{j, k}$. In other words, all the soil or field properties that could affect yield response to N are embedded in the simulated parameters.

The spatial distributions of cell-level parameters $\alpha_{j, k}$, $\beta_{j, k}$, $\gamma_{j,k}$, $\tau_{j, k}$, and the error term $\varepsilon_{j, k}$ were simulated by generating spatially correlated random fields using unconditional Gaussian geostatistical simulation based on the specified variograms [@dietrich1996fast, @wood1994simulation], and the simulation processes were conducted using the R package gstat [@graler16]. Specifically, the model is spherical, the nugget variance is zero, and the range is 600 meters. The nugget value of zero means that infinitesimally close observations have a zero covariance (i.e., they are identical). The range of 600m means that observations separated by more than 600m are spatially uncorrelated. A higher range value indicates increased spatial dependence, meaning less abrupt differences are observed between the production function parameters of neighboring cells. The mean and sill variance of each parameter were specified to result in a realistic mean yield of $11,416$ kg ha$^{-1}$, and such that the cells' true economically optimal N rate ranged from $113$ kg ha$^{-1}$ to $273$ kg ha$^{-1}$ among all the simulations, a range into which most real-world N rate recommendations fall [e.g., @sawyer2018]. Note that the range of the optimal N rates of individual rounds of simulations are narrower. In defining the magnitude of the error term, we utilized the experimental data generated through eight on-farm randomized N field trials conducted by the Data-Intensive Farm Management Project (DIFM) project in 2018 [@bullock2019data]. Using the data from each of the eight actual trials, separate regressions of yield on N were run, and standard deviations of the residuals were calculated. The mean value of the eight standard deviations was $1370$ kg ha$^{-1}$, which was the square root value of the sill variances assigned to the simulations' error terms.

@@

Letting $p$ represent the crop price and $w$ represent the price of nitrogen fertilizer, in each simulation the "true" economically optimal N rate for each cell $(j, k)$ was calculated as

$$
N^*_{j,k} \equiv argmax_N \Big[p\cdot f_{j,k}(N)-w\cdot N\Big].
$$

@@

In each simulation, for each cell $(j, k)$, the simulation's true yield $y_{j, k}$ was generated based on the cell's assigned application rate $N_{j,k}$, true response parameters $c_{j,k} = (\alpha_{j,k}, \beta_{j,k}, \gamma_{j,k}, \tau_{j,k})$, and error term $\varepsilon_{j,k}$. This procedure generated a field-level, cell-specific data set, $\{(y_{j, k},N_{j, k} ):j=1,\dots,1440;k=1,\dots, 6 \}$. To maintain consistency with real-world OFPEs, it was assumed that harvesting equipment could only record yields accurately at an 18m $\times$ 12m (subplot) resolution. Since every cell in a plot received the same N application rate, then so did every cell within a subplot, so $N_{j,1} = N_{j,2}= \dots = N_{j,6} = N_j$ for each subplot $j$. Letting $\mu_j$ denote the mean of the yields of the cells in subplot $j$, the analysis of each round's data was based on 1440 $(\mu_j,N_j )$ observations.

@@

$$\Pi^{*SCAM} = 1/8640 \sum_{j=1}^{1440} \sum_{k=1}^6 \big[pf_{j, k} (\hat{N}^{*SCAM})-w\hat{N}^{*SCAM}\big]$$

where $f_{j, k}(\cdot)$ denotes the true yield response function at cell $(j, k)$.

@@

$$\Pi^{GWR}=1/8640 \sum_{j=1}^{1440} \sum_{k=1}^6 [pf_{j, k} (\hat{N}^{*GWR}_j)-w\hat{N}^{*GWR}_j]$$

where $f_{j, k} (\hat{N}^{*GWR}_j)$ denote the true yield generated at cell $(j, k)$ with subplot $j$'s GWR estimated N rate.

@@

$$\hat{\Pi}^{*SCAM} = 1/8640 \sum_{j=1}^{1440} \sum_{k=1}^6 \big[p\hat{f}^{GWR}_{j, k} (\hat{N}^{*SCAM} )-w\hat{N}^{*SCAM}\big]$$

$$\hat{\Pi}^{*GWR}=1/8640 \sum_{j=1}^{1440} \sum_{k=1}^6 [p\hat{f}^{GWR}_{j, k} (\hat{N}^{*GWR}_{j} )-w\hat{N}^{*GWR}_{j}]$$

@@

Our results clealy show it can be dangerous to use GWR with quadratic functional form when yield-input relationship is quadratic plateau as done in @trevisan2021spatial. Their choice of quadratic functional form is likely due to the fact there is no readily usable statistical software or package that implements non-linear GWR. The only non-linear model available at the moment is the linear-plateau GWR by @lambert2022geographically. Unfortunately, economically optimal input rate cannot be adjusted according to price using linear-plateau model as the economically optimal input rate occurs always at the kink. Given that many yield-input relationships follow quadratic-plateau functional form for many crops, it would be fruitful to develop a GWR method with quadratic-plateau functional form. It should be also possible and interesting to build semi-parametric GWR where the yield response functions are estimated without assuming particular functional forms (like SCAM). It is also noted that the recently developed multi-scale GWR model [@fotheringham2017multiscale; @yu2020inference; @comber2022route] allows the bandwidth to be derived separately for each covariate in the model, which would potentially improve the performances of GWR estimates and be incorporated into future research. Please note, however, that multi-scale GWR models are not necessary in our simulations as we have only one covariate ($N$) in our simulations.

Most important, whether using GWRT or GWRR, researchers must be cautious about their estimated value of VRA when model is assumed to be quadratic when the true underlying yield-input response is quadratic-plateau in relity. Our results show that it is likely that they will over-estimate their true values and the bias can be misleadingly high with non-negligible probability. The extremely high values of VRA reported in @trevisan2021spatial are likely to have reflected this bias. Indeed, the bias problem we have raised here is likely to be observed for other statistical methods as well because the bias comes from the assumption that the _estimated_ yield response functions are true. Whatever the underlying statistical methods for yield response functions may be, researchers are likely to overestimate the true value of their methods. It would be an interesting future research to investigate the bias in other commonly used statistical methods in the literature on site-specific yield response estimation (such as regression with interaction terms of field characteristics, machine learning, and more) by using a similar simulation-based evaluation approach as done in this study.

Finally, it would be interesting to examine the pure performance of GWR. The objecive of this article was to evaluate GWR with quadratic functional form when the true yield-input relationship is quadratic-plateau. Therefore, we evaluated GWR when model is misspecified in a particular manner. Once, GWR with quadratic-plateau model is developed, it would be interesting to see how it performs when the true yield reponse to input is quadratic-plateau. In this case, there is no functional form misspecification and the pure ability of GWR can be isolated.

>>>>

However, deploying sophisticated sensors to gather field characteristics data is also costly, and the effects of their generation and use on farming profitability remains in question [@gardner2021economic]. Recognizing the significant costs of obtaining useful, high-resolution soil and field properties data, @trevisan2021spatial demonstrated a method of providing site-specific management recommendations without such data. They estimated site-specific yield response functions by applying GWR techniques on data from OFPEs [@bullock2019data], and reported dramatic results, estimating an average potential gain of \$65 ha$^{-1}$ from applying seed and N at optimal uniform rates (instead of at the rates the farmers would have chosen if not participating in the research), and an additional potential gain of \$58 ha$^{-1}$ when changing from optimal uniform application rates to optimal site-specific application rates. This is rather surprising given the often-reported poor statistical accuracy of GWR estimates [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation] and also much lower value of variable rate application over uniform rate application reported in previous studies [@bullock1998does; @thrikawala1999economic; @koch2004economic]. @rakshit2020 also applied GWR to on-farm experiment data. However, while they did estimate site-specific yield response functions, they did not derive site-specific economically optimal nitrogen rates based on them, and thus did not conduct economic analysis, unlike @trevisan2021spatial. @evans2020assessment explored using GWR with a linear model specification to detect low- and high-response areas, but like @rakshit2020, they also did not estimate site-specific economically optimal nitrogen rates.

@@

The primary objective of this study is examine the degree and direction of bias in the estimation of the economic value of GWR-based site-specific nitrogen rate recommendations (or "variable rate application", VRA) when GWR model is specified as quadratic when the true yield response function follows the quadratic-plateau functional form. We evaluate two sets of GWR quadratic specifications used in @rakshit2020 and @trevisan2021spatial. Both of them assumed a quadratic response of yield to nitrogen rate ($N$). However, while @trevisan2021spatial estimated the coefficient on $N^2$ as a global parameter, @rakshit2020 estimated it locally for each point. At first, it appears that the specification used by @rakshit2020 is superior since it is more flexible than the specification used by @trevisan2021spatial. However, the flexibility can be a disadvantage rather than an advantage because the estimation of economically optimal nitrogen rate (EONR) is highly sensitive to the coefficient estimates on $N^2$, and GWR often provides inaccurate local estimation of that coefficient. It is critical to keep in mind that it is not our objective to measure the bias in the coefficient estimation by GWR, unlike [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation]. Rather, we are interested in the economic implications of the statistical inaccuracy in estimating the coefficients of the model in this study. As part of identifying bias in the estimation of the economic value of VRA based on the GWR approaches, we evaluate their actual values. Finally, we also evaluate their relative performances compared to uniform rate application (URA) based on shape-constrained additive model approach. It should be noted that the economical optimization in this study only involves farmers' private profit, while the environmental externalities (such as fertilizer runoff and leaching) are not considered.

@@

The field was 432m (72 cells) wide and 864m (144 cells) long, making its area 37.3 ha. Data from the 6-m-long headlands, side-lands (there are no transition zones on the north and south ends of the field), and 12-m-wide "transition zones" were not included in the data analyzed. In total there were 1440 subplots available for experimental data analysis. The index $j \in {1, 2, \dots, 1440}$ identifies the field's subplots, and the index $i \in {1, \dots , 6}$ identifies the cells within a subplot. The couplet $(j, i)$ is used to identify individual cells.

@@

An extensive literature examines the choice of functional form in yield response estimation [@cerrato1990comparison, @frank1990comparison, @bullock1994quadratic, @tembo2008crop]. Our simulation assume that each cell $(j, i)$'s "true" yield response function is assumed to follow the commonly-used quadratic-plateau functional form:

$$
\begin{equation} \tag{1}
y_{j,i} = f_{j,i} (N) = f(N, c_{j,i}) = 
  \begin{cases}
  \alpha_{j,i} + \beta_{j,i} N + \gamma_{j,i} N^2 + \varepsilon_{j,i} \, ,& N < \tau_{j,i} \\
  \alpha_{j,i} + \beta_{j,i} \tau_{j,i} + \gamma_{j,i} \tau_{j,i}^2 + \varepsilon_{j,i} \, ,& N \ge \tau_{j,i}
  \end{cases}
\end{equation}
$$

where $c_{j,i} = (\alpha_{j,i},\beta_{j,i},\gamma_{j,i},\tau_{j,i})$ is the vector of yield response function parameters. $\tau_{j,i}$ can be interpreted as the critical value of N rate at which cell $(j, i)$'s yield reaches its plateau, where yield no longer increases with N rate. $\varepsilon_{j, i}$ is a stochastic error term. The quadratic-plateau functional form implies a diminishing marginal product of N until a yield plateau, which are desirable properties for a yield response function [@frank1990comparison] and a pattern commonly observed in agronomic studies. Note that the cell-specific yield response function $f_{j, i} (N)$ is the reduced form of the meta response function $f$ when the characteristics vector takes on the value $c_{j, i}$. In other words, all the soil or field properties that could affect yield response to N are embedded in the simulated parameters.

The spatial distributions of cell-level parameters $\alpha_{j, i}$, $\beta_{j, i}$, $\gamma_{j,i}$, $\tau_{j, i}$, and the error term $\varepsilon_{j, i}$ were simulated by generating spatially correlated random fields using unconditional Gaussian geostatistical simulation based on the specified variograms [@dietrich1996fast, @wood1994simulation], and the simulation processes were conducted using the R package gstat [@graler16]. Specifically, the model is spherical, the nugget variance is zero, and the range is 600 meters. The nugget value of zero means that infinitesimally close observations have a zero covariance (i.e., they are identical). The range of 600m means that observations separated by more than 600m are spatially uncorrelated. A higher range value indicates increased spatial dependence, meaning less abrupt differences are observed between the production function parameters of neighboring cells. The mean and sill variance of each parameter were specified to result in a realistic mean yield of $11,416$ kg ha$^{-1}$, and such that the cells' true economically optimal N rate ranged from $113$ kg ha$^{-1}$ to $273$ kg ha$^{-1}$ among all the simulations, a range into which most real-world N rate recommendations fall [e.g., @sawyer2018]. Note that the range of the optimal N rates of individual rounds of simulations are narrower. In defining the magnitude of the error term, we utilized the experimental data generated through eight on-farm randomized N field trials conducted by the Data-Intensive Farm Management Project (DIFM) project in 2018 [@bullock2019data]. Using the data from each of the eight actual trials, separate regressions of yield on N were run, and standard deviations of the residuals were calculated. The mean value of the eight standard deviations was $1370$ kg ha$^{-1}$, which was the square root value of the sill variances assigned to the simulations' error terms.

@@

Letting $p$ represent the crop price and $w$ represent the price of nitrogen fertilizer, in each simulation the "true" economically optimal N rate for each cell $(j, i)$ was calculated as

$$
N^*_{j,i} \equiv argmax_N \Big[p\cdot f_{j,i}(N)-w\cdot N\Big].
$$

@@

In each simulation, for each cell $(j, i)$, the simulation's true yield $y_{j, i}$ was generated based on the cell's assigned application rate $N_{j,i}$, true response parameters $c_{j,i} = (\alpha_{j,i}, \beta_{j,i}, \gamma_{j,i}, \tau_{j,i})$, and error term $\varepsilon_{j,i}$. This procedure generated a field-level, cell-specific data set, $\{(y_{j, i},N_{j, i} ):j=1,\dots,1440;k=1,\dots, 6 \}$. To maintain consistency with real-world OFPEs, it was assumed that harvesting equipment could only record yields accurately at an 18m $\times$ 12m (subplot) resolution. Since every cell in a plot received the same N application rate, then so did every cell within a subplot, so $N_{j,1} = N_{j,2}= \dots = N_{j,6} = N_j$ for each subplot $j$. Letting $\mu_j$ denote the mean of the yields of the cells in subplot $j$, the analysis of each round's data was based on 1440 $(\mu_j,N_j )$ observations.

@@

$$\Pi^{*SCAM} = 1/8640 \sum_{j=1}^{1440} \sum_{k=1}^6 \big[pf_{j, i} (\hat{N}^{*SCAM})-w\hat{N}^{*SCAM}\big]$$

where $f_{j, i}(\cdot)$ denotes the true yield response function at cell $(j, i)$.

@@

$$\Pi^{GWR}=1/8640 \sum_{j=1}^{1440} \sum_{k=1}^6 [pf_{j, i} (\hat{N}^{*GWR}_j)-w\hat{N}^{*GWR}_j]$$

where $f_{j, i} (\hat{N}^{*GWR}_j)$ denote the true yield generated at cell $(j, i)$ with subplot $j$'s GWR estimated N rate.

@@

$$\hat{\Pi}^{*SCAM} = 1/8640 \sum_{j=1}^{1440} \sum_{k=1}^6 \big[p\hat{f}^{GWR}_{j, i} (\hat{N}^{*SCAM} )-w\hat{N}^{*SCAM}\big]$$

$$\hat{\Pi}^{*GWR}=1/8640 \sum_{j=1}^{1440} \sum_{k=1}^6 [p\hat{f}^{GWR}_{j, i} (\hat{N}^{*GWR}_{j} )-w\hat{N}^{*GWR}_{j}]$$

@@

It is worthy of mentioning that, in most previous studies of model comparisons the model performances were predominantly measured by statistical accuracy of parameter estimates (such as bias, mean squared error, type I error, confidence intervals, and so on), for either the GWR models [@lu2017geographically, @harris2019simulation] or the econometric models in general [@christopeit2006local, @su2016identifying]. While the statistical measures are fundamental criteria to evaluate model performances, what matters more in economic practices are whether and how much those statistical accuracy can translate into the ultimate economic values. Particularly, the magnitudes of this translation may depend on the application scenarios. This study differs from previous literature in that it reports the economic value of specific econometric models (GWR) with model functional form misspecification (quadratic estimation while the truth is quadratic-plateau) when being used in specific applications (corn site-specific nitrogen management) and under specific conditions (normal-sized production field, various market price scenarios, etc.) through a simulation-based approach.

It is worth noting that previous studies comparing models have predominantly focused on measuring model performance based on statistical accuracy of parameter estimates, such as bias, mean squared error, type I error, and confidence intervals, for both GWR models [@lu2017geographically; @harris2019simulation] and general econometric models [@christopeit2006local, @su2016identifying]. While these statistical measures are fundamental for evaluating model performance, in practical economic applications it is imperative to consider the translation of statistical accuracy into economic value. Moreover, the extent of this translation could vary depending on the specific application scenarios. This study distinguishes itself from previous literature by explicitly examining the economic value of specific econometric models (GWR) under a model functional form misspecification (quadratic instead of quadratic-plateau), in a specific application (corn site-specific nitrogen management), and under specific context scenarios (normal-sized production field, various market prices, etc.), through a simulation-based methodology. We encourage other model comparison studies in empirical economic research to also incorporate similar assessment of economic value.

Our results clearly show it can be dangerous to use GWR with quadratic functional form when yield-input relationship is quadratic plateau as done in @trevisan2021spatial. Their choice of quadratic functional form is likely due to the fact that there is no readily usable statistical software or package that implements non-linear GWR. The only non-linear model available at the moment is the linear-plateau GWR by @lambert2022geographically. Unfortunately, economically optimal input rate cannot be adjusted according to price using linear-plateau model as the economically optimal input rate occurs always at the kink. Given that many yield-input relationships follow quadratic-plateau functional form for many crops, it would be fruitful to develop a GWR method with quadratic-plateau functional form. It should be also possible and interesting to build semi-parametric GWR where the yield response functions are estimated without assuming particular functional forms (like SCAM). It is also noted that the recently developed multi-scale GWR model [@fotheringham2017multiscale; @yu2020inference; @comber2022route] allows the bandwidth to be derived separately for each covariate in the model, which would potentially improve the performances of GWR estimates and be incorporated into future research. Please note, however, that multi-scale GWR models are not necessary in our simulations as we have only one covariate ($N$) in our simulations.
